Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-14 prob.tex
prob.tex \section{Classical Probability Spaces} Review and see how to add new things...

There is however another more subtle assumption of unbounded
computational power in the experiment. We are assuming that we can
always determine with certainty whether a needle is crossing a
line. But ``lines'' on the the floor have thickness, their distance
apart is not exactly $h$, and the needles lengths 
are not all absolutely equal to $\ell$. These perturbations make
the events ``fuzzy.'' Thus, in an experiment with limited resources,
it is not possible to talk about the idealized event that exactly $M$
needles cross lines as this would require the most expensive needles
built to the most precise accuracy, laser precision for drawing lines
on the floor, and the most powerful microscopes to determine if a
needle does cross a line. Instead we might talk about the event that
$M-\delta$ needles evidently cross lines and $M+\delta'$ needles
plausibly cross lines where $\delta$ and $\delta'$ are
resource-dependent approximations. This fuzzy notion of events leads
to probabilities being only calculable within intervals of confidence
reflecting the certainty of events and their plausibility. This is
indeed consistent with published experiments: in an experiment with
$3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872},
$1213$ needles clearly crossed a line and $11$ needles were close
enough to plausibly be considered as crossing the line: we would
express the probability in this case as the interval
$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we
are certain that the event has probability at least
$\frac{1213}{3204}$ but it is possible that it would have probability
$\frac{1224}{3204}$.

@@

\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
space~$\Omega$ and its event~$\events$, a function~$\mu:\events\rightarrow[0,1]$
is a classical interval-valued probability measure if and only if
$\mu$ satisfies the following conditions: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
and 
\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly
intervals. 
\end{itemize}
\qed\end{lemma}

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.\footnote{\yutsung{If we want to use convex, we need to explain the physical
meaning of convex interval-valued probability measures...? If there
is a good explanation, we may only consider convex interval-valued
probability measures, and replace the definition in the beginning...?}}
\end{itemize}
\qed\end{definition}

>>>>

There is however another more subtle assumption of unbounded computational
power in the experiment. We are assuming that we can always determine
with certainty whether a needle is crossing a line. But ``lines''
on the the floor have thickness, their distance apart is not exactly
$h$, and the needles' lengths are not all absolutely equal to $\ell$.
These perturbations make the events ``fuzzy.'' Thus, in an experiment
with limited resources, it is not possible to talk about the idealized
event that exactly $M$ needles cross lines as this would require
the most expensive needles built to the most precise accuracy, laser
precision for drawing lines on the floor, and the most powerful microscopes
to determine if a needle does cross a line. Instead we might talk
about the event that $M-\delta$ needles evidently cross lines and
$M+\delta'$ needles plausibly cross lines where $\delta$ and $\delta'$
are resource-dependent approximations. This fuzzy notion of events
leads to probabilities being only calculable within intervals of confidence
reflecting the certainty of events and their plausibility. This is
indeed consistent with published experiments: in an experiment with
$3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872},
$1213$ needles clearly crossed a line and $11$ needles were close
enough to plausibly be considered as crossing the line: we would express
the probability in this case as the interval $\left[\frac{1213}{3204},\frac{1224}{3204}\right]$
expressing that we are certain that the event has probability at least
$\frac{1213}{3204}$ but it is possible that it would have probability
$\frac{1224}{3204}$.

@@

\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
space~$\Omega$ and its event~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
and 
\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly
intervals. 
\end{itemize}
\qed\end{lemma}

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex} or \emph{2-monotone} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\end{itemize}
\qed\end{definition}
